Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex
last version

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
  \caption{A screenshot of the guidance interface showing a waypoint (based on an 3D Android model), the object scanner area and the guidance instruction arrows. }\label{fig:system-screenshot}
\end{figure}

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The grid is generated at the app's start-up and remains constant throughout its lifetime. The app then uses the new waypoint's location to provide the user with guidance instructions. The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

By recording the previous positions and waypoint locations the app generated, it can infer the state values for $v$ and $n$. Furthermore, the camera provides the ID of the object in view, populating $o$ in the state. A real-time object detector was not used in this system to avoid unnecessary complexity and processing overhead and encoded QR codes and barcode scanner library were used to simulate object detection instead.

The QR code scanner requires raw image data. To avoid scanning multiple QR codes and using excess processing power by scanning large images, we only used the centre part of the screen to scan for a barcode. This scanner area is $300\times300$ pixels and scans for barcodes without causing any frame-rate drops.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{figures/system_screenshot2.png}
  \caption{A screenshot of the guidance interface showing an example of guidance instructions towards a waypoint and the QR-object scanner area.}\label{fig:system-screenshot}
\end{figure}

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: the radial grid is only used to discretise the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The grid is generated at the app's start-up and remains constant throughout its lifetime. The app then uses the new waypoint's location to provide the user with guidance instructions. The policy actions, and waypoints by extension, are given relatively to the current camera's pan-tilt orientation.

By recording the previous positions and waypoint locations, the system can infer the state values for $n$ and $v$ described in Section~\ref{sec:states}. Furthermore, the camera provides the ID of current object in view, which is assigned to the state variable $o$. As explained in the next section, we did not use a real object detector in our experiments, but we simulated it with 7 different QR codes, one for each object's type, and a camera-based QR scanner from the Android's machine learning API (MLKit).

The QR scanner requires raw image data. To avoid scanning multiple QR codes and speed up the image processing, we only used the central part of the camera's frame, which is $300\times300$ pixels. This choice defines also the precision required in pointing the camera towards the object (see also Figure~\ref{fig:system-screenshot}).
